---
title: Efficient R Programming
author: xiaoyu
date: '2020-09-06'
slug: efficient-r-programming
categories:
  - notes
tags:
  - book
draft: yes
---
```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```
Here are some tips and thoughts while reading the book([Efficient R programming](https://csgillespie.github.io/efficientR/introduction.html#what-is-efficiency)).

# Introduction

```{r}
library("microbenchmark")
library("profvis")
library("ggplot2")
```

- touch typing & work consistently.
- it's better to use `packagename::function` if you only use a package's function once.
- benchmark & profiling.
  - `microbenchmark(), compare different function working speed.`
  - profilling: testing large chunks of code.
- `installr::updateR()`
- install and loading several packages:
```{r eval=FALSE}
pkgs = c("raster", "leaflet", "rgeos") # package names
install.packages(pkgs)
inst = lapply(pkgs, library, character.only = TRUE)

```
- 
```{r eval=FALSE}
update.packages()
```

- Project management is very important!
```
project/
  - README.Rmd # Project description
  - set-up.R  # Required packages
  - R/ # For R code
  - input # Data files
  - graphics/
  - output/ # Resultss
```